%Introduction
\section{Introduction}
	A Confidential Cloud Service is an additional service that can be applied on top of an existing cloud provider \cite{confidentiality}. These confidential services are needed, if properties have requirements of safety, which cannot be guranteed by a normal cloud provider. One example of service, that can be added on a cloud to make it confidential is the Confidential Consortium Framework (CCF) \cite{Howard}. It wants to guarantee the CIA requirements (confidentiality, integrity and availability) on multiparty applications.  \\
	 The CIA triade explains three important requirements of information security \cite{ciaBook} \cite{cia}. It contains data confidentiality, Integrity protection and high availability. Data confidentiality is keeping the data private, which is very important especially for cloud providers. Challenges are encrypting the data and protecting the keys. Integrity protection is introduced as a requirement for data confidentiality. It is the ensurance of complete and correct code that is not changed by a bad party. But these two characteristics are hard to implement although they are mandatory for cloud computing. This is, because in clod computing the trusted computing base (TCB) gets bigger, so applications in the field of finances, medicine or governmental issues cannot afford to trust this whole TCB. High availability is required by the fact the people rely on the systems thatare on the cloud. So they should work, even if failures occur.